%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj + some brand new features from Blagoi Dimitrov
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{makecell}
\usepackage[link=off]{phonenumbers}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{tikz}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage[margin=0.3in]{geometry}
% Adjust margins
\addtolength{\oddsidemargin}{-0.0in}
\addtolength{\evensidemargin}{-0.0in}
\addtolength{\textwidth}{0in}
\addtolength{\topmargin}{5pt}
\addtolength{\textheight}{0.0in}

\urlstyle{same}

\usepackage{xcolor}% http://ctan.org/pkg/xcolor
\usepackage{hyperref}% http://ctan.org/pkg/hyperref
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  linkbordercolor=red,
  urlcolor=blue!70!black
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\def \ifempty#1{\def\temp{#1} \ifx\temp\empty }

\newcommand{\resumeItem}[2]{
  \item\small{
  	\ifempty{#1}#2\else\textbf{#1}{: #2 \vspace{-2pt}}\fi
  }
}

\definecolor{mygray}{gray}{0}
\usepackage{fancybox}

\usepackage{lmodern}
\usepackage{tikz}

% Style definition
\tikzset{rndblock/.style={rounded corners,rectangle,draw,outer sep=0pt}}

% Command Definition
% 1 optional to customize the aspect, 2 mandatory: text to be framed
\newcommand{\tframed}[2][]{\tikz[baseline=(h.base)]\node[rndblock,#1] (h) {\color{black}{#2}};}

\newcommand*{\mystrut}{\rule[-0.2\baselineskip]{0pt}{0.8\baselineskip}}
\newcommand{\skill}[1]{\tframed[lightgray]{\mystrut#1}}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeExpSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
      {\scriptsize#5}
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeProjSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \scriptsize {#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{changepage}
\newcommand{\resumeDesc}[1]{\begin{adjustwidth}{5pt}{0pt}\vspace{-2pt}{\small{#1}}\end{adjustwidth}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\definecolor{bondiblue}{rgb}{0.0, 0.50, 0.0}
\definecolor{ceruleanblue}{rgb}{0.16, 0.32, 0.75}
\definecolor{brandeisblue}{rgb}{0.0, 0.44, 1.0}
\definecolor{bleudefrance}{rgb}{0.19, 0.55, 0.91}
\definecolor{azure(colorwheel)}{rgb}{0.0, 0.5, 1.0}

%----------HEADING-----------------
\begin{center}
  \textbf{\Huge BLAGOI DIMITROV } \\
  \faGithub~\href{https://github.com/anarsiel}{\color{blue}anarsiel} $\vert$
  \faEnvelope~\href{mailto:blagoi_dimitov@icloud.com}{\color{blue}blagoi\textunderscore dimitov@icloud.com} $\vert$
  \faPhoneSquare~{\color{blue}\texttt{+}7\,(921)\,849\texttt{-}22\texttt{-}90} \\
\end{center}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
        \resumeExpSubheading
      {Lipt-Soft~\href{https://www.lipt-soft.ru}{\color{blue}\faGlobe}}{St. Petersburg, Russia}
      {SWE, Online banking for Bank Saint-Petersburg team}{Oct. 2021 - Dec. 2021}
      {\skill{Kotlin} \skill{Testing} \skill{Fin-Tech} }
      \resumeDesc{
      \begin{itemize}
          \item Developed the currency conversion service for online banking.
          \item Studied microservice architecture.
      \end{itemize}}
  
      \resumeExpSubheading
      {Yandex~\href{https://en.wikipedia.org/wiki/Yandex}{\color{blue}\faInfoCircle}}{St. Petersburg, Russia}
      {SWE Intern, Yandex.Cloud Managed Service for Kubernetes team}{Sept. 2020 - March 2021}
      {\skill{Kubernetes} \skill{GoLang} \skill{Docker} \skill{Protobuf}}
      \resumeDesc{
      \begin{itemize}
          \item Implemented the SLI (Service Level Indicator) metrics measurement tool \\ based on international SLI practices for Kubernetes.
          \item Suggested my own version of SLA, based on SLI.
      \end{itemize}}
      
      \resumeExpSubheading
      {Wärtsilä~\href{https://www.wartsila.com/}{\color{blue}\faGlobe}~\href{https://en.wikipedia.org/wiki/Wartsila}{\color{blue}\faInfoCircle}}{St. Petersburg, Russia}
      {SWE Intern, Spatial Data Preparation Technologies team}{July 2019 - Jan. 2020}
      {\skill{Comp. Geometry} \skill{Vector Cartography}  \skill{Protobuf} \skill{C\texttt{+}\texttt{+}} \skill{SCRUM}}
      \resumeDesc{
      \begin{itemize}
          \item Implemented vector cartography in C\texttt{+}\texttt{+} and replaced raster cartography with it.
          \item { Result: the maps have reduced their volume by 70\%}
      \end{itemize}
      }
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
       {ITMO University ~\href{https://en.itmo.ru/}{\color{blue}\faGlobe}~\href{https://en.wikipedia.org/wiki/ITMO_University}{\color{blue}\faInfoCircle}}{St. Petersburg, Russia}
      {Master's degree in Digital Transformation strategies and technologies}{Sept. 2022 - Aug. 2024 (present)}
  
    \resumeSubheading
       {Yandex School of Data Analysis ~\href{https://academy.yandex.com/dataschool/}{\color{blue}\faGlobe}}{St. Petersburg, Russia}
       {Machine Learning, Software Engineering and Computer Science courses. \textbf{GPA: 4.5}}
       {Sept. 2019 - Aug. 2024 (Present)}
  
    \resumeSubheading
       {ITMO Financial Management Courses.~\href{https://cdpo.itmo.ru/financy}{\color{blue}\faGlobe}}{St. Petersburg, Russia}
       {Professional training courses}
       {March 2021 - June 2022}
       
    % \resumeSubheading
    %   {HSE GMAT Courses.~\href{https://spb.hse.ru/humart/lang/komkursy/gmat}{\color{blue}\faGlobe}}{St. Petersburg, Russia}
    %   {Advanced preparation for the International GMAT exam. Level B2.}
    %   {March 2021 - June 2021}
       
    \resumeSubheading
       {ITMO University ~\href{https://en.itmo.ru/}{\color{blue}\faGlobe}~\href{https://en.wikipedia.org/wiki/ITMO_University}{\color{blue}\faInfoCircle}}{St. Petersburg, Russia}
      {Bachelor's degree in Computer Science and Applied Math. \textbf{GPA: 4.2}}{Sept. 2018 - Aug. 2022}
  \resumeSubHeadingListEnd
  
%--------PROGRAMMING SKILLS------------
\section{International Certificates}
 \resumeSubHeadingListStart
    \resumeSubheading
       {GMAT. Score 640~\href{https://disk.yandex.ru/i/dLAUkSPzI8jIxw}{\color{blue}\faFilePdfO}}{}
       {Integrated Reasoning: \textbf{7/8}, Analytical Writing: \textbf{4/6}}
       {Aug. 2021}
       
  \resumeSubheading
       {FCE. B2~\href{https://disk.yandex.ru/i/PeTsyT2lbEXGhQ}{\color{blue}\faFilePdfO}}{}
       {Score: \textbf{177}}
       {July 2018}
 \resumeSubHeadingListEnd


% Projects
\section{Projects}
  \resumeSubHeadingListStart
      \resumeProjSubheading
      {Marketplace Of Services\href{https://github.com/anarsiel/Marketplace-Of-Services/blob/master/Project Decription.pdf}{\color{blue}~\faGithub}}{}
      {\skill{Databases} \skill{PostgreSQL} \skill{ERM} \skill{PDM} \skill{Triggers} \skill{Database normalization} }{Jan. 2022}
          \resumeDesc{Designing a database for a service marketplace}
        
    \resumeProjSubheading
      {BoringBooking\href{https://github.com/anarsiel/BoringBooking}{\color{blue}~\faGithub}}{}
      {\skill{Swift} \skill{iOS-Dev} \skill{MVC} \skill{Secure Athentication} \skill{Databases} }{Dec. 2021}
          \resumeDesc{Service for table reservation in restaurants.  \\ The key feature is the ability to choose a specific table according to it's characteristics}
  
      \resumeProjSubheading
      {Let It Charge\href{https://docs.google.com/presentation/d/1hdVm4wCiyvsL261TjihCfd5usS6mde-TsPwuAKniE5Q/edit?usp=sharing}{\color{blue}~\faFilePowerpointO}}{}
      {\skill{Market analysis} \skill{Marketing} \skill{Pitching}}{May 2021}
          \resumeDesc{Project for the deployment of a network of charging stations for electric vehicles in parking lots}
  
      \resumeProjSubheading
      {BIDE\href{https://github.com/anarsiel/BIDE}{\color{blue}~\faGithub}}{}
      {\skill{Python} \skill{QML}}{May 2020}
          \resumeDesc{IDE for my own DSL programming language with syntax highlighter.
          
          Language has convenience in developing modules and working with them and an advanced compilator/interpretator with \\ human-readable error messages and variables that make the language both imperative and declarative.}
          
          

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
  \item{
     \textbf{Programming Languages}{: Python, Kotlin, C\texttt{+}\texttt{+}, Java, Assembly, GoLang, SQL.}
  }\vspace{-7pt}
  \item{
     \textbf{Technologies}{: Mock Testing, Unit-Testing, GTest, Git, \LaTeX, Docker. }
  }
  \vspace{-7pt}
  \item{
     \textbf{Knowledge}{: Database design, Algorithms and Data Structures, Computer Architecture, iOS-Dev,  MVC, Client-Server apps}
  }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}